Differential Analysis

### 2018-11-19 da_test.Rmd
Stratify per condition

# T3 vs T7
```{r, cache=TRUE}
ggtopi_subs <-subset_samples(gg_topi, timepoint %in% c('T3','T7'))
ggtopi_subs.genus <- tax_glom(ggtopi_subs,taxrank = "Genus")
ggtopi_subs.genus.relab <- transform_sample_counts(ggtopi_subs.genus, function(x) x/sum(x))
mmtx <- model.matrix(object = ~timepoint + timepoint:real_vaccine + timepoint:real_bifido + timepoint:real_vaccine:real_bifido, data = data.frame(ggtopi_subs@sam_data))
idx <- which(apply(mmtx, 2, function(x) all(x==0)))
mmtx <- mmtx[,-idx]

@@

  otu_ab_t37 <- otu_table(ggtopi_subs)[rownames(res37.filt), t37_samples_idx] %>%
              data.frame %>%
              tibble::rownames_to_column("OTU") %>%
              tidyr::gather_("SampleID", "Abundance", setdiff(colnames(.), "OTU")) %>%
              mutate(timepoint=stringr::str_sub(.$SampleID,12, 13))

@@

### Dotplot log2FC vs Genus
```{r}
res37.filt %>% as.data.frame %>% 
  cbind(as.matrix(tax_table(ggtopi_subs.genus)[rownames(res37.filt),])) %>%
  ggplot(aes(log2FoldChange, interaction(Family, Genus))) + 
  geom_vline(xintercept = 0.0, color = "gray", size = 0.5) +
  geom_point(size=3, aes(color = baseMean)) + 
  facet_grid(Phylum ~ ., scales = "free", space = "free_y",switch = "y",as.table = T)+
  theme_bw() +
  scale_y_discrete(position = "right") +
  theme(axis.text = element_text(hjust = 0, vjust=0.5, size = 11),
        strip.text = element_text(size = 9),
        axis.title = element_text(size = 9),
        axis.title.y = element_blank(),
        strip.background = element_rect(colour = "transparent", fill = "transparent"),
        strip.text.y = element_text(angle = 180)
  )
```

@@

>>>>

# T3 vs T7
```{r, cache=TRUE}
ggtopi_subs <-subset_samples(gg_topi, timepoint %in% c('T3','T7'))
ggtopi_subs.relab <- transform_sample_counts(ggtopi_subs, function(x) x/sum(x))
ggtopi_subs.genus <- tax_glom(ggtopi_subs,taxrank = "Genus")
ggtopi_subs.genus.relab <- transform_sample_counts(ggtopi_subs.genus, function(x) x/sum(x))
mmtx <- model.matrix(object = ~timepoint + timepoint:real_vaccine + timepoint:real_bifido + timepoint:real_vaccine:real_bifido, data = data.frame(ggtopi_subs@sam_data))
idx <- which(apply(mmtx, 2, function(x) all(x==0)))
mmtx <- mmtx[,-idx]

@@

  otu_ab_t37 <- otu_table(ggtopi_subs.relab)[rownames(res37.filt), t37_samples_idx] %>%
              data.frame %>%
              tibble::rownames_to_column("OTU") %>%
              tidyr::gather_("SampleID", "Abundance", setdiff(colnames(.), "OTU")) %>%
              mutate(timepoint=stringr::str_sub(.$SampleID,12, 13))

  otu_ab_t37 %>% bind_cols(data.frame(tax_table(ggtopi_subs.relab)[otu_ab_t37$OTU,c('Phylum','Family','Genus')])) %>%
  ggplot() +
    geom_boxplot(aes(interaction(Family, Genus), Abundance, fill=timepoint)) + 
    facet_grid(Phylum ~ ., scales = "free", space = "free_y", as.table= T)+
    coord_flip() + 
    theme(strip.background = element_rect(colour = "transparent", fill = "transparent"),
        strip.text.y = element_text(angle = 0))
```

@@

@@

### Boxplot of Genus abundances of differenitally abundant Genera
```{r}
  genus_ab_t <- otu_table(ggtopi_subs.genus.relab)[rownames(res37.filt), ] %>%
              data.frame %>%
              tibble::rownames_to_column("OTU") %>%
              tidyr::gather_("SampleID", "Abundance", setdiff(colnames(.), "OTU")) %>%
              mutate(timepoint=stringr::str_sub(.$SampleID,12, 13)) %>%
              mutate(condition= if_else(timepoint=='T3','',stringr::str_sub(.$SampleID,4, 6)))

  genus_ab_t %>% bind_cols(data.frame(tax_table(ggtopi_subs.genus.relab)[genus_ab_t$OTU,c('Phylum','Family','Genus')])) %>%
  ggplot() +
    geom_boxplot(aes(interaction(Family, Genus), Abundance, fill=interaction(timepoint, condition))) + 
    facet_grid(Phylum ~ ., scales = "free", space = "free_y", as.table= T)+
    coord_flip() + 
    theme_bw() +
    theme(strip.background = element_rect(colour = "transparent", fill = "transparent"),
        strip.text.y = element_text(angle = 0))
```
